Module analysis

### 2023-01-31 report/module_analysis.Rmd
Add modules + Z variation

@@

```{r}
mod %>%
  filter(rho == 0.5, env_stoch == .9) %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
  geom_boxplot() +
  facet_grid(rows = vars(stab), scales = "free_y")

```

>>>>

### low Stochasticity (sigma = .5)

```{r}
mod %>%
  filter(rho == 0, env_stoch == .5) %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
  geom_boxplot() +
  facet_grid(rows = vars(stab), scales = "free_y")
```

```{r}
mod %>%
  filter(rho == 0.5, env_stoch == .5) %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
  geom_boxplot() +
  facet_grid(rows = vars(stab), scales = "free_y")
```

```{r}
mod %>%
  filter(rho == 1, env_stoch == .5) %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
  geom_boxplot() +
  facet_grid(rows = vars(stab), scales = "free_y")
```

### low Stochasticity (sigma = .9)

@@

```{r}
mod %>%
  filter(rho == 0.5, env_stoch == .9) %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
  geom_boxplot() +
  facet_grid(rows = vars(stab), scales = "free_y")
```
